\iffalse
\documentclass[12pt]{article}
\usepackage{graphicx}
%\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage[none]{hyphenat}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}   % for having text in math mode
\usepackage{listings}
\usepackage{gensymb}
\lstset{
  frame=single,
  breaklines=true
}
%New macro definitions
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\let\vec\mathbf

\begin{document}
\begin{center}
\textbf\large{CLASS-12\\CHAPTER-6 \\ Application of Derivatives}
\end{center}

\section*{EXERCISE - 6.3}
\section*{Short Answer (S.A.)}
\fi
\begin{enumerate}
\item At what point ,the slope of the curve $y=-x^3+3x^2+9x-27$ is maximum? Also find the maximum slope.
\item prove that f (x)=sinx+$\sqrt{3}$ cosx has maximum value at $x=\frac{\pi}{6}$
	\section*{Long Answer (L.A)}
\item If the sum of the lengths of the hypotenuse and a side of a right angled triangle is given, show that the area of the triangle is maximum when the angle between them is $\frac{\pi}{3}$
\item Find the points of local maximal, local minima and the points of inflection of the function f (x)=$x^5-5x4+5x^2-1$. Also find the corresponding local maximam and local minimum values
\item A telephone company in a town has 500 subscribers on its and collects fixed charges of RS 300/- per subscriber per year. The company proposes to increase the annual subscription and it is belived that fog every increase of Re1/. one subsariber will discontinue the serice. find what increase will bring maximum profit?
\item If the straight line x casoc+y sno oc=P touches the curve $\frac{x^2}{a^2}+\frac{y^2}{b^2}=1$ ,\text{then prove that} $a^2 \cos^{2}\alpha+b^2 \sin^{2}\alpha=P^2$.
\item An open box with square base is to be made of a given quantity of card board of area $c^2$. show that the maiximum volume of the box is $\frac{c^23}{6\sqrt{3}}$cubic units.
\item Find the bimensions of the rectangle of perimeter 36cm which will sweep out a volume as large as possible, when revolved about one of its sides. Also find the maximum voiume.
\item lf the sum of the surface areas of cube and a sphere is constant, what is the ratio of on edge of the cube to the diameter of the sphere when the sum of their volumes is minimum?
\item AB is a diameter of a circle and c is any point on the circle show that the area of $\triangle$ABC is maximum, when it is isosceles,
\item A metal box with a square base and vertical sides is to contain $1024 cm^3$ The material for the top and bottom casts $RS 5/cm^2$ and the material for the sides costs Rs$2.50/cm^2$.Find the least cost of the box.
\item The sum of the surface areas of a rectangular parallelopiped with sides x,2x and $\frac{x}{3}$ and a sphere is given to be constant. prove that the sum of their volumes is minimum, if x is equal to three times the radius of the sphere Also find the minimum value of the sum of their volumes
\item The least value of the function f (x)=ax+$\frac{b}{x}$(a$>$0,b$>$0,x$>$0) is \makebox[1cm]{\hrulefill}
\item if x is real ,the minimum value of $x^2-8x+17$is
\begin{enumerate}
\item -1
\item 0
\item 1
\item 2
\end{enumerate}
\item The smallest value of the polynomial $x^3-18x^2+96x$ in [0,9] is
\begin{enumerate}
\item 126
\item 0
\item 135 
\item 160
\end{enumerate}
\item The function f (x)=$2x^3-3x^2-12x+4$ has
\begin{enumerate} 
\item two points of local maximum
\item two points of local minimum
\item one maxima and one minima
\item no marima or minima
\end{enumerate}
\item The maximum volue of sin x casx is 
\begin{enumerate} 
\item $\frac{1}{4}$
\item $\frac{1}{2}$
\item $\sqrt{2}$
\item $2\sqrt{2}$
\end{enumerate}
\item At x =5$\frac{\pi}{6}$ f (x)=2 sin3x+3 cosx
\begin{enumerate} 
\item maximum
\item minimum
\item zero
\item neither maximum nor minimum
\end{enumerate}
\item maximum slope of the curve y=$-x^3+ 3x^2+9x-27$ is
\begin{enumerate} 
\item 0
\item 12
\item 16
\item 32 
\end{enumerate}
\item f (x)=$x^2$ has a stationary point at
\begin{enumerate}
\item x=e
\item x=$\frac{1}{e}$
\item x=1
\item x=$\sqrt{e}$
\end{enumerate}
\item The maximum value of [$\frac{1}{x}$] is
\begin{enumerate}
\item e
\item $e^e$
\item $e^\frac{1}{e}$
\item $\frac{1}{e}^\frac{1}{e}$
\end{enumerate}
\end{enumerate}
